Exciting Internal Gravity Waves, Toy Problem

### 2018-03-23 presentations/Su_GM_032318.tex
check in final presentation

\begin{frame}
    \frametitle{Problem Setup}
    \framesubtitle{Problem Statement}
    \begin{itemize}
        \item 2D hydrodynamics with driving boundary condition, produce gravity
            waves.
        \item Begin with linear incompressible case, equations:
        \begin{subequations}\label{se:eom}
            \begin{align}
                \pd{\rho_1}{t} &= 0,\\
                \vec{\nabla} \cdot \vec{u}_1 &= 0,\\
                \pd{\vec{u}_1}{t} &= -\frac{\vec{\nabla}P_1}{\rho_0} + \vec{g}.
            \end{align}
        \end{subequations}

@@

        \item Wavelike solutions $u_{1z} \propto e^{z/2H}e^{i\p*{k_xx + k_zz -
            \omega t}}$, $u_{1x}, P_1, \rho_1$ similar up to phase and terms
            $\sim \mathcal{O}\p*{H^{-1}}$.

@@

    \begin{itemize}
        \item Linear incompressible hydrodynamics with periodic BCs in $x$,
            driving term at $z = 0$ and either Dirichlet or reflection-free BCs
            at $z = L_z$.

        \item Spectral code Dedalus, built-in Runge-Kutta timestepper (simplest
            to characterize).
    \end{itemize}
\end{frame}

@@

    \begin{figure}[!h]
        \centering
        \begin{subfigure}{0.4\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_0.png}
        \end{subfigure}
        \begin{subfigure}{0.4\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_1.png}
        \end{subfigure}

        \begin{subfigure}{0.4\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_2.png}
        \end{subfigure}
        \begin{subfigure}{0.4\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_3.png}
        \end{subfigure}
        \caption{Agreement of numerical and analytical solution at four adjacent
        snapshots.}\label{fig:sponge_agree}
    \end{figure}
\end{frame}

@@

    \begin{itemize}
        \item $RMS = \frac{\sqrt{\sum\limits_{x, z, t} \p*{u_{1z}^{(N)}(x, z, t)
            - u_{1z}^{(2N)}(x, z, t)}^2}}{\sqrt{
            \sum\limits_{x, z, t} \p*{u_{1z}^{(N)}(x, z, t)}^2}}$
    \end{itemize}
    \begin{figure}[!h]
        \centering
        \begin{subfigure}{0.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat_conv/t_conv.png}
        \end{subfigure}
        \begin{subfigure}{0.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat_conv/x_conv.png}
        \end{subfigure}

        \begin{subfigure}{0.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat_conv/z_conv.png}
        \end{subfigure}
        \caption{Convergences of time stepsize and grid resolution. Note the
        power law convergence in timestep but exponential in $z$ points (since
        $x$ is always monochromatic, increasing resolution does little).}\label{fig:convsv}
    \end{figure}
\end{frame}

>>>>

\begin{frame}
    \frametitle{Problem Setup}
    \framesubtitle{Problem Statement}
    \begin{itemize}
        \item Eventual objective: simulate IGW breaking in WDs, compute
            energy/angular momentum dissipation profiles.
        \item Toy problem: 2D hydrodynamics with driving boundary condition.
        \item Begin with linear incompressible case, equations:
        \begin{subequations}\label{se:eom}
            \begin{align}
                \pd{\rho_1}{t} &= 0,\\
                \vec{\nabla} \cdot \vec{u}_1 &= 0,\\
                \pd{\vec{u}_1}{t} &= -\frac{\vec{\nabla}P_1}{\rho_0} + \vec{g}.
            \end{align}
        \end{subequations}

@@

        \item Wavelike solutions $u_{1z} \propto e^{z/2H}e^{i\p*{k_xx + k_zz -
            \omega t}}$, $u_{1x}, P_1, \rho_1$ similar up to phase and terms
            $\sim \mathcal{O}\p*{H^{-1}} \ll k_z$.

        \item Obeys dispersion relation
            \begin{equation}
                \omega^2 = \frac{N^2k_x^2}{k_x^2 + k_z^2 + \frac{1}{4H^2}}.
            \end{equation}

@@

    \begin{itemize}
        \item Linear incompressible 2D hydrodynamics with periodic BCs in $x$,
            driving term at $z = 0$ and either Dirichlet or reflection-free BCs
            at $z = L_z$.

        \item Spectral code Dedalus, exponential convergence for shock-free
            hydrodynamics.
    \end{itemize}
\end{frame}

@@

    \begin{figure}[!h]
        \centering
        \begin{subfigure}{0.37\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_0.png}
        \end{subfigure}
        \begin{subfigure}{0.37\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_1.png}
        \end{subfigure}

        \begin{subfigure}{0.37\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_2.png}
        \end{subfigure}
        \begin{subfigure}{0.37\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat/agree_plots/sponge_3.png}
        \end{subfigure}
        \caption{Agreement of numerical and analytical solution at four adjacent
        snapshots.}\label{fig:sponge_agree}
    \end{figure}
\end{frame}

@@

    \begin{itemize}
        \item $RMS_i = \frac{\sqrt{\sum\limits_{x, z, t} \p*{u_{1z}^{(i)}(x, z,
            t) - u_{1z}^{(N)}(x, z, t)}^2}}{\sqrt{ \sum\limits_{x, z, t}
            \p*{u_{1z}^{(N)}(x, z, t)}^2}}$
    \end{itemize}
    \begin{figure}[!h]
        \centering
        \begin{subfigure}{0.37\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat_conv/x_conv.png}
        \end{subfigure}
        \begin{subfigure}{0.37\textwidth}
            \centering
            \includegraphics[width=\textwidth]{../sims/2d_strat_conv/z_conv.png}
        \end{subfigure}
        \caption{Convergences of RMS over grid resolution. Note the exponential
        convergence in $z$ to machine precision (since $x$ is always
        monochromatic, increasing resolution does little).}\label{fig:convsv}
    \end{figure}
\end{frame}
